---
title: "Lab 00 - Hello IDS!"
author: "SITI FATIMAH BINTI YUSOF"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("fatimah", "echo", "annie", "justin", "peter"),
  github_username = c("fatimahyusof", "GLDDPJ", "echo-xingyu","Anniexyc","Apollo0417" ), 
  colour = c("springgreen4", "green", "blue", "yellow", "cyan"),
  hobby = c("Hiking", "Hiking", "Muay Thai","snowboarding", "History"),
  favourite_number = c(1, 10, 24, 5, 21)
 )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

*anniexyc likes the number 5 and yellow colour*
*apollo0417 favorite colour is cyan and loves the number *
*fatimahyusof likes number*


### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "username", 
          y = "favorite number",
          title = "idk")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
